Descriptive analysis of Solanaceae

### 2018-06-07 summarystats/solanaceaedescriptivev2.Rmd
results SSE polyploidy

---
title: "Descriptive analysis of Solanaceae"
author: "Rosana Zenil-Ferguson"
date: "4/20/2018"
output:
  html_document: default
  pdf_document: default
---
```{r,error=FALSE, message=FALSE, warning=FALSE}
library("knitr")
setwd('~/Dropbox/solploidy/basicdata')
library("ape")
library("phytools")
library("treeplyr")

>>>>

---
title: "Descriptive analysis of Solanaceae"
author: "Rosana Zenil-Ferguson"
date: "4/20/2018"
#last modified 06/06/2018
output:
  html_document: default
  pdf_document: default
---
```{r,error=FALSE, message=FALSE, warning=FALSE}
library("knitr")
setwd('~/Dropbox/solploidy')
library("ape")
library("phytools")
library("treeplyr")
